An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
Figures are changed with grayscale versions

\author{
Can Erhan\supit{a}, 
Evangelos Sariyanidi\supit{b}, 
Onur Sencan\supit{c}, 
Hakan Temeltas\supit{c}
\skiplinehalf
\supit{a}Istanbul Technical University Mechatronics Engineering Department, Maslak 34469, Istanbul, Turkey; 
\supit{b}Centre of Intelligent Sensing, Mile End Road, E1 4NS, London, U.K.;
\supit{c}Istanbul Technical University Control and Automation Engineering Department, Maslak 34469, Istanbul, Turkey
}

>>>>

\author{
Can Erhan\supit{a}, 
Evangelos Sariyanidi\supit{b}, 
Onur Sencan\supit{a}, 
Hakan Temeltas\supit{a}
\skiplinehalf
\supit{a}Istanbul Technical University Control and Automation Engineering Department, \\
Maslak 34469, Istanbul, Turkey; \\
\supit{b}Centre of Intelligent Sensing, Mile End Road, E1 4NS, London, U.K.
}
